\subsection{\hspace{-65pt}Honors}
\cventry{Apr. 2021}{Victor K. LaMer Award}{American Chemical Society Colloids Division}{}{}{}\vspace{-2pt}
\cventry{Feb. 2019}{Biointerfaces Institute Student Innovator Award}{University of Michigan (UM)}{}{}{}\vspace{-2pt}
\cventry{Oct. 2018}{Towner Award for Graduate Research}{}{Honorable Mention}{}{}\vspace{-2pt}
\cventry{Oct. 2018}{Charles G. Overberger Award for Excellence in Research}{UM}{}{}{}\vspace{-2pt}
\cventry{Jan. 2018}{North Campus Martin Luther King Spirit Award}{UM}{}{}{}\vspace{-2pt}
\cventry{Oct. 2017}{Nonna Hamilton Student Service Award}{UM}{}{}{}\vspace{-2pt}
\cventry{2016, 2017}{Prof. Albert and Mrs. Yee Student Leadership Award}{UM}{}{}{}\vspace{-2pt}
\cventry{April 2017}{Chapter of the Year}{American Chemical Society POLY/PMSE}{}{}{}\vspace{-2pt}
\cventry{May 2014}{Commencement Speaker}{UConn}{}{}{}\vspace{-2pt}
\cventry{May 2014}{Outstanding Academic Achievement Award, School of Engineering}{UConn}{}{}{}\vspace{-2pt}
\cventry{2013}{Marshall Scholarship Finalist}{}{}{}{}\vspace{-2pt}
\cventry{2013}{Rhodes Scholarship Nominee}{}{}{}{}\vspace{-2pt}
\cventry{2012-2014}{New England Scholar}{UConn}{}{}{}\vspace{-2pt}
\cventry{2011}{Babbidge Scholar}{UConn}{}{}{}\vspace{-2pt}
\cventry{2010-2014}{Dean's List}{UConn}{}{}{}\vspace{-2pt}

\subsection{\hspace{-65pt}Fellowships and Scholarships}
\cventry{2018-2019}{Rackham Predoctoral Fellowship}{UM}{}{}{}\vspace{-2pt}
\cventry{Dec. 2017}{Science Communication Fellow, Museum of Natural History}{UM}{}{}{}\vspace{-2pt}
\cventry{July 2014}{Michigan Institute for Computational Discovery and Engineering Fellowship}{UM}{}{}{}\vspace{-2pt}
\cventry{2014-2018}{Rackham Merit Fellowship}{UM}{}{}{}\vspace{-2pt}
\cventry{2013-2014}{GE Advanced Materials Endowment Scholarship}{UConn}{}{}{}\vspace{-2pt}
\cventry{2012-2013}{Art McEvily Academic Scholarship}{UConn}{}{}{}\vspace{-2pt}
\cventry{2010-2014}{Academic Excellence Scholarship}{UConn}{}{}{}

\subsection{\hspace{-65pt}Travel Awards}
\cventry{Jul. 2018}{National Science Foundation FOMMS Travel Award}{National Science Foundation}{}{}{}\vspace{-2pt}
\cventry{Jan. 2018}{Ovshinsky Student Travel Award}{Americal Physical Society}{}{}{}\vspace{-2pt}
\cventry{Jan. 2018}{DCOMP Travel Award}{Americal Physical Society}{}{}{}\vspace{-2pt}

\subsection{\hspace{-65pt}Presentation Awards}
\cventry{Dec. 2019}{Poster Award}{Materials Research Society}{}{}{}\vspace{-2pt}
\cventry{Apr. 2017}{2\textsuperscript{nd} Place, Student Presentations}{Materials Research Society}{}{}{}\vspace{-2pt}
\cventry{Nov. 2016}{3\textsuperscript{rd} Place, Student Posters}{Engineering Graduate Symposium}{}{}{}\vspace{-2pt}
\cventry{Apr. 2016}{3\textsuperscript{rd} Place, Student Posters}{MICDE Symposium}{}{}{}\vspace{-2pt}
\cventry{Oct. 2015}{1\textsuperscript{st} Place, Student Presentations}{Macromolecular Science and Engineering Symposium}{}{}{}\vspace{-2pt}
